%------------------------
% AI-Optimized Resume Template
% Optimized for automatic resume processing systems
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for better parsing
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% SECTION FORMATTING - Clear, consistent headers
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% COMMANDS - Optimized for AI parsing
\newcommand{\email}[1]{\faEnvelope\ \href{mailto:#1}{#1}}
\newcommand{\phone}[1]{\faPhone\ \href{tel:#1}{#1}}
\newcommand{\linkedin}[2][]{\faLinkedin\ \href{#2}{#1}}
\newcommand{\github}[2][]{\faGithub\ \href{#2}{#1}}
\newcommand{\name}[1]{ \centerline{\Huge\scshape\bfseries{#1}} }

% Standardized item format for consistent parsing
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Standard job entry format
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

% Job title within same company - clear hierarchy
\newcommand{\resumeJobTitle}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small\bfseries#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

% Subsequent job titles with tighter spacing
\newcommand{\resumeJobTitleTight}[2]{
  \vspace{-8pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small\bfseries#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

% Company header for multiple positions
\newcommand{\resumeCompanyHeader}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

% Project format with clear structure
\newcommand{\project}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeBullet}[1]{\item\small{#1}}

{\renewcommand\labelitemi{}

\newcommand{\resumeItemListStart}{ \begin{itemize}[leftmargin=*] }
\newcommand{\resumeItemListEnd}{ \end{itemize} }

\newcommand{\resumeBulletStart}{ \begin{itemize}[leftmargin=*, itemsep=0pt, before={\linespread{0.9}\selectfont}] }
\newcommand{\resumeBulletEnd}{\end{itemize}}

\begin{document}

% HEADING - Clear contact information structure
\name{Steven DeFalco}
\begin{center}
    \email{stevencdefalco@gmail.com} \textperiodcentered\ 
    \phone{732-778-4102} \textperiodcentered\ 
    \linkedin[Steven DeFalco]{https://www.linkedin.com/in/stevendefalco/} \textperiodcentered\ 
    \github[StevenDeFalco]{https://github.com/StevenDeFalco}    
\end{center}

% EDUCATION - Structured format for degree parsing
\section{Education}
  \resumeItemListStart
    \vspace{-1pt}\item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{Stevens Institute of Technology} & Hoboken, NJ \\
        \textit{\small MBA \& MS in Applied Artificial Intelligence} & \textit{\small January 2025 -- May 2026} \\
        \textit{\small BS in Computer Science, Highest Honors (GPA: 3.86)} & \textit{\small September 2021 -- December 2024} \\
      \end{tabular*}\vspace{-5pt}

    \vspace{-1pt}\item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{Marine Academy of Science and Technology} & Highlands, NJ \\
      \end{tabular*}\vspace{-5pt}
  \resumeItemListEnd

% EXPERIENCE
\section{Experience}
  \resumeItemListStart

    % TCE
    \resumeCompanyHeader{TCE}{Great Neck, NY}

    % AI Solutions Engineer
    \resumeJobTitle{AI Solutions Engineer}{May 2025 - Present}
    \resumeBulletStart
      \resumeBullet
      {Led end-to-end redesign of an Azure-native AI chatbot for internal engineers, executives, and estimators---integrating query rewriting and hybrid semantic/vector retrieval (Azure AI Search, OpenAI API, Python, LlamaIndex). Boosted \emph{good-answer rate} from 50\% $\rightarrow$ 98\% and \emph{answer rate} from 74\% $\rightarrow$ 98\% on a 100-query A/B test, enabling rapid access to insights across hundreds of sensitive contract and technical documents, ensuring data privacy compliance.}
      \resumeBullet
      {Fully rebuilt document ingestion \& RAG pipeline (LlamaParse $\rightarrow$ Markdown, custom chunking, embeddings; Azure Blob + SQL; Azure AI Search index), increasing \emph{top-1 citation relevance rate} from 32\% $\rightarrow$ 76\% and \emph{highlight accuracy rate} from 10\% $\rightarrow$ 56\%. Collaborated with non-technical stakeholders to define requirements and present results.}
      \resumeBullet
      {Designed, developed, and deployed a tunnel-clearance calculator PWA in Ionic/React (TypeScript) for offline field use, replacing manual and paper-based clearance checks. Enabled in-field safety verification for MTA-regulated tunnel installations, reducing turnaround and mitigating risk of costly compliance violations. Delivered native-like UX with offline caching, in-app updates, and CSV export in owner-specified format, hosted on Azure.}
    \resumeBulletEnd

    % Innovation Engineering Intern
    \resumeJobTitleTight{Innovation Engineering Intern}{May 2024 - August 2024}
    \resumeBulletStart
      \resumeBullet
      {Automated migration of 1,000+ internal LMS courses using Python (Pandas, APIs, Playwright), eliminating manual effort and proving a scalable automation approach.}
      \resumeBullet
      {Built Azure Timer Functions to sync HR and LMS data in near real time, enabling accurate mass training assignments.}
      \resumeBullet
      {Delivered a secure React portal for hosting site drone imagery, providing open team access and avoiding licensing costs.}
    \resumeBulletEnd

    % SOFTWARE TESTING INTERNSHIP
    \resumeCompanyHeader{Pixel Light Digital Media}{Lyndhurst, NJ}
    \resumeJobTitle{Software Testing \& Quality Assurance Analyst}{June 2022 - August 2022}
    \resumeBulletStart
      \resumeBullet
      {Led testing of real-time computer vision system for convention booth engagement tracking; improved distance prediction accuracy to within 2 ft. in 50 ft. range. Produced business insights using 51k+ data points to optimize booth layouts and increase marketing ROI. Collaborated with developers to deliver stability and reliability to enterprise clients.}
    \resumeBulletEnd

    % COURSE ASSISTANT 
    \resumeCompanyHeader{Stevens Institute of Technology}{Hoboken, NJ}
    \resumeJobTitle{Computer Science Course Assistant}{September 2022 - May 2023}
    \resumeBulletStart
      \resumeBullet
      {Led labs for Data Structures courses with live coding and personalized instruction, contributing to a 98\% pass rate.}
    \resumeBulletEnd

  \resumeItemListEnd

% PROJECTS - Clear project structure
\section{Projects} 
  \resumeItemListStart

    % predictMLB
    \resumeSubItem{\href{https://twitter.com/predictmlb}{@predictMLB} (Summer 2023)}
    {Built and deployed an autonomous X/Twitter bot on AWS Lightsail (Python, MLBStats-API, cron) that posts same-day MLB game predictions using a custom LightGBM model trained on over 5 years of historical data with fully automated data pipelines, achieving 66\% predictive accuracy on a 1,100-game backtest.}
  
  \resumeItemListEnd

% COURSEWORK - Structured format
\section{Coursework}
  \resumeItemListStart
    \item{
        NLP, Computer Vision, Deep Learning, Database Management, Statistics, Data Structures \& Algorithms
      }
  \resumeItemListEnd

% SKILLS & TECHNOLOGIES - Categorized for better parsing
\section{Skills and Technologies}
  \resumeItemListStart
    \item{
      \textbf{Languages}{: Python, SQL, TypeScript, JavaScript}
      \\
      \textbf{Technologies}{: Azure, Azure AI Search, Azure Functions, Azure AI Foundry, OpenAI API, LlamaIndex/LlamaParse, LLMs, MCPs, Ionic/React (PWA), Git, CI/CD, Linux, Prompt Engineering, LaTeX}
    }
  \resumeItemListEnd

% EXTRACURRICULARS - Clear structure
\section{Leadership \& Community}
  \resumeItemListStart
    \resumeSubItem{Vice-President of Alpha Sigma Phi (Alpha Tau)}
    {
      Led a 40-member chapter; oversaw ~25 events/semester; achieved a 91\% median attendance rate; coordinated event logistics and scheduling; oversaw conflict resolution.
    }
  \resumeItemListEnd

\end{document}
