%------------------------
% Adapted from a template by Sourabh Bajaj (https://github.com/sb2nov/resume)
% Additional inspiration from Bill Ryan (https://github.com/billryan/resume)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% SECTION FORMATTING
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


% COMMANDS
\newcommand{\email}[1]{\faEnvelope\ \href{mailto:#1}{#1}}
\newcommand{\phone}[1]{\faPhone\ \href{tel:#1}{#1}}
\newcommand{\linkedin}[2][]{\faLinkedin\ \href{#2}{#1}}
\newcommand{\github}[2][]{\faGithub\ \href{#2}{#1}}
\newcommand{\name}[1]{ \centerline{\Huge\scshape{#1}} }

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\project}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeBullet}[1]{\item\small{#1}}

{\renewcommand\labelitemi{}

\newcommand{\resumeItemListStart}{ \begin{itemize}[leftmargin=*] }
\newcommand{\resumeItemListEnd}{ \end{itemize} }

\newcommand{\resumeBulletStart}{ \begin{itemize}[leftmargin=*, itemsep=0pt, before={\linespread{0.9}\selectfont}] }
\newcommand{\resumeBulletEnd}{\end{itemize}}


\begin{document}


% HEADING
\name{Steven DeFalco}
\begin{center}
    \email{stevencdefalco@gmail.com} \textperiodcentered\ 
    \phone{732-778-4102} \textperiodcentered\ 
    \linkedin[StevenDeFalco]{https://www.linkedin.com/in/stevendefalco/} \textperiodcentered\ 
    \github[StevenDeFalco]{https://github.com/StevenDeFalco}    
\end{center}


% EDUCATION
\section{Education}
  \resumeItemListStart
    \resumeSubheading
      {Stevens Institute of Technology}{Hoboken, NJ}
      {Bachelors of Science in Computer Science,  GPA: 3.86}{Sep. 2021 -- Present}
    \resumeSubheading
      {Marine Academy of Science and Technology}{Highlands, NJ}
      {GPA: 96.5/100, Activities: Key Club, National Honor Society, NJROTC}{Sep. 2017 -- Jun. 2021}
  \resumeItemListEnd


% EXPERIENCE
\section{Experience}
  \resumeItemListStart

    % COURSE ASSISTANT 
    \resumeSubheading
      {Stevens Institute of Technology}{Hoboken, NJ}
      {Computer Science Course Assistant}{Sep. 2022 - Present}
      \resumeBulletStart
        \resumeBullet
        {Instruct undergraduate students in "Introduction to Computer Science" and "Data Structures" courses.}
        \resumeBullet
        {Collaborate with peers and the professor to design and maintain a comprehensive curriculum for 15-week semesters.}
        \resumeBullet
        {Conduct weekly lab sessions and office hours to demonstrate concepts and facilitate task-based learning; used over 25 carefully-crafted assignments to reinforce student understanding of material; contributed to 98\% pass rate.}
%        \resumeBullet
%        {Held bi-weekly office hours, offering individualized explanations and practice tailored to students' needs, which contributed to a 98\% pass rate among enrolled students.}
      \resumeBulletEnd
  
    % SOFTWARE TESTING INTERNSHIP
    \resumeSubheading
      {Pixel Light Digital Media}{Lyndhurst, NJ}
      {Software Testing \& Quality Assurance Analyst}{Jun. 2022 - August 2022}
      \resumeBulletStart
        \resumeBullet
        {Designed and conducted tests on subsequent software iterations of a real-time, artificial intelligence system to be used in a published app used to track foot traffic, dwell time, and interaction with convention booths.}
        \resumeBullet
        {Tested distance prediction accuracy of the software with faces in 3-Dimensional space using variable conditions.}
        \resumeBullet
        {Accomplished a 400\% increase in relative accuracy of A.I. distance prediction while spearheading the testing. }
        \resumeBullet
        {Final product predicts a distance which is within an average 2 feet of the true value (within effective 50 foot range).}
        \resumeBullet
        {Tracked over 51,000 impressions across 3-day commercial deployment using product; analyzed dwell time and location to provide client feedback with the goal of optimizing booth interactivity and attention given to primary displays. }
      \resumeBulletEnd

  \resumeItemListEnd


% PROJECTS 
\section{Projects} 
  \resumeItemListStart

    % predictMLB
    \resumeSubItem{\href{https://twitter.com/predictmlb}{predictMLB} (Summer 2023)}
    {Independent project in which I developed and deployed an autonomous Twitter bot that publishes same-day MLB game winner predictions using a deep learning model and runs on AWS Lightsail \\
    Used: \emph{Python, AWS, Git, LightGBM, MLB Stats-API, Twitter API, Concurrent Programming, APScheduler}}
      \resumeBulletStart
        \resumeBullet 
        {Designed and developed object-oriented infrastructure to request player/team data from MLB Stats-API and odds data from Odds-API; constructs each game as an individual training sample in the format of a pandas Series}
        \resumeBullet 
        {Optimized and scaled features to prepare for training, fine-tuned LightGBM boosting framework for binary classification task, tuned hyperparameters to maximize accuracy}
        \resumeBullet 
        {Trained model using 6,300 samples, achieved 66\% accuracy on unseen testing set of 1100 samples}
        \resumeBullet 
        {Engineered Python script to run as background process on an AWS Lightsail Linux instance, uses \emph{cron-like} scheduling to run recurring subprocesses that request upcoming games and predict using the trained model, games are scheduled and tweeted through the Twitter API to \href{https://twitter.com/predictmlb}{@predictMLB}}
      \resumeBulletEnd
  
  \resumeItemListEnd


% COURSEWORK
\section{Coursework}
  \resumeItemListStart
    \resumeSubItem{Deep Learning}
    {Graduate-level course with a focus on the design and implementation of modern deep learning models. \\ Learned: \emph{Neural Network Design, Computer Vision, Natural Language Processing} \hfill Used: \emph{TensorFlow, Keras, Python}}
    \resumeSubItem{Software Development Process} 
    {Course covering the essentials of developing better software in less time. \\ Learned: \emph{Development Life Cycles, Archiecture and Design, Development Methoodoliges} \hfill Used: \emph{GitLab, C++, OOP}}

%    \resumeSubItem{Systems Programming}
%    {Course covering essentials of systems programming in C on UNIX systems. \\ Learned: \emph{Version Control, Network Protocol, UNIX Syscall Interface, Inter-Process Communication} \hfill Used: \emph{C, Bash}}

    \resumeSubItem{Operating Systems}
    {Course covering the internals and programming interface of modern operating systems. \\ Learned: \emph{Processes, Concurrency, Programming with Threads, Memory Management} \hfill Used: \emph{Linux Kernel, C, Debian}}

%    \resumeSubItem{Algorithms}
%    {Course covering design, analysis, and implementation of modern algorithms. \\ Learned: \emph{Space-time analysis; Algorithm Design; Graph, Numerical, Search, and Sorting Algorithms} \hfill Used: \emph{C++}}
%    \resumeSubItem{Data Structures}
%    {Course covering the design, implementation, and use cases of the fundamental data structures. \\ Learned: \emph{Complexity, Abstract Data Types, Testing, Trees, Maps, Sorting} \hfill Used: \emph{Java, JUnit}}

    \resumeSubItem{Other}
%    {Statistics, Linear Algebra, Discrete Mathematics, Principles of Programming Languages, Computer Architecture}
    {Algorithms, Data Structures, Statistics, Linear Algebra, Discrete Math, Prog. Languages, Comp. Architecture}
  \resumeItemListEnd


% SKILLS & TECHNOLOGIES
\section{Skills and Technologies}
  \resumeItemListStart
    \item{
      \textbf{Languages}{: Python, C/C++, Java, Bash, R}
      \hfill
      \textbf{Technologies}{: Git, AWS, Latex}
    }
  \resumeItemListEnd


% EXTRACURRICULARS
\section{Extracurriculars}
  \resumeItemListStart
    \resumeSubItem{Alpha Sigma Phi Fraternity}
    {Vice-President of the Alpha Tau chapter of the Alpha Sigma Phi national fraternity. \\
    Responsible for overseeing and coordinating all events, promoting effective communication, leading conflict resolution.}
  \resumeItemListEnd

\end{document}}
